---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  cache = TRUE
)
```
# lockeutils

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip) [![Travis build status](https://travis-ci.org/lockedata/lockeutils.svg?branch=master)](https://travis-ci.org/lockedata/lockeutils) [![Coverage status](https://coveralls.io/repos/github/lockedata/lockeutils/badge.svg)](https://coveralls.io/r/lockedata/lockeutils?branch=master)

The goal of lockeutils is to provide some common tools to the Locke Data team.

## Installation


``` r
remotes::install_github("lockedata/lockeutils")
```

At the first package loading, `lockeutils` should guide you to install fonts. We'll update instructions here based on your experience.

## ggplot2 theme

```{r}
library("ggplot2")
library("lockeutils")
df <- data.frame(
gp = factor(rep(letters[1:3], each = 10)),
y = rnorm(30)
)
ggplot(df, aes(gp, y)) +
  geom_point() +
  ggtitle("wow title LHS great",
          subtitle = "nice plot") +
  theme_ld()

```

## colour scale 

For no more than 3 classes.

```{r}

ggplot(mtcars, aes(factor(cyl), fill = factor(vs))) +
geom_bar() +
theme_ld() +
scale_fill_ld()

ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
  geom_point() +
  theme_ld() +
   scale_color_ld()
```

## Colours on their own

```{r}
lockeutils::get_ld_colours()
```

## Contributing

Wanna report a bug or suggest a feature? Great stuff! For more information on how to contribute check out [our contributing guide](.github/CONTRIBUTING.md). 

 Please note that this R package is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this package project you agree to abide by its terms.
